Multi-target detection with application to cryo-electron microscopy

### 2019-06-03 InverseProblemsV2/inverse_problems_v2_highlighted.tex
submitted files

In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.

>>>>

In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$, and the noise level $\sigma$ for generic $x$.
